Chum Populations

### 2015-06-25 paper/main.tex
synteny, Ne, and paper updates

\documentclass[12pt,  one column]{article}
\usepackage{graphicx}

@@

\section*{Abstract}

\section*{Introduction}

@@

Dominance coding \cite{}

 - measure information loss

\subsection*{Ascertainment Bias}

@@

table (supplemental)
paralogs
note the distribution of paralogs matches the  pattern found in other salmonids
syntenic relationships - per LG
Table (supplemental?)
Population genetics

@@

\includegraphics[scale=.3]{figures/PCA_dom_paralogs.png}
\includegraphics[scale=.3]{figures/PCA_codom_subsample.png}

@@

\section*{Discussion}

@@

%\includegraphics[scale=.4]{figures/supplemental/ascertainment.png}

\includegraphics[scale=.4]{figures/supplemental/PCA_eigenvalues.png}

%\includegraphics[scale=.4]{figures/supplemental/TW_stats.png}

>>>>

\documentclass[12pt,  one column]{article}
\usepackage{graphicx}
\usepackage{float}

@@

Does this turn into two papers?

 - linkage map and individual-based analyses - including duplicated loci

 - inference of adaptation - life history variation  - Fst across the genome.

\section*{Abstract}
To do

\section*{Introduction}
To do

Expected population structure

ESA listing - summer chum ESU

Salmonid WGD

@@

\subsection*{Linkage map}

Sequence analysis and genotyping

Identification of paralogs follows Waples (2015)

Map construction follows Waples (2015)

Synteny - relation to genetic resources
\begin{itemize}
	\item Chinook salmon
    \item Atlantic salmon
\end{itemize}

\subsection*{Population Genetics}
Sequence analysis and genotyping

Genotyping duplicate loci using the dominance coding suggested by Patterson (2006). 
Individual-based analyses
\begin{itemize}
	\item PCAs - How do compare? - maybe measure info loss?
    \item Heterozygosity
	\item Fst across the genome
\end{itemize}

Population-based analyses
\begin{itemize}
	\item MAF, Heterozygosity
	\item Fst across the genome
    \item Effective population size - Waples and Do
    \item Bayescan outlier tests
\end{itemize}

@@

table (supplemental)
paralogs
note the distribution of paralogs matches the  pattern found in other salmonids
syntenic relationships - per LG
Table (supplemental?)

\subsection*{Population Genetics}

@@

\includegraphics[scale=.3]{figures/PCA_dom_paralogs.png}
\includegraphics[scale=.3]{figures/PCA_codom_subsample.png}
\subsection*{Population Genetics}

@@

\section*{Discussion}
To do

@@

\begin{figure}[H]
\includegraphics[scale=.3]{figures/supplemental/ascertainment.png}
\caption{Minor allele frequency distribution for all genotyped loci (blue) and just the loci placed on the linkage map (green). The increase in MAF shows the effect of ascertainment bias.}
\end{figure}

\begin{figure}[H]
\includegraphics[scale=.4]{figures/supplemental/PCA_eigenvalues.png}
\caption{Percent variance explained (eigenvalue) for the first eight PC axes of each locus set.  Notice the similarity between the two bi-allelic sets and the two haplotypic sets.}
\end{figure}

\begin{figure}[H]
\includegraphics[scale=.4]{figures/supplemental/PCA_eigenvalues.png}
\caption{Percent variance explained (eigenvalue) for the first eight PC axes of each locus set.  Notice the similarity between the two bi-allelic sets and the two haplotypic sets.}
\end{figure}

\begin{figure}[H]
\includegraphics[scale=.4]{figures/supplemental/TW_stats.png}
\caption{Number of significant PC axes as determined by the Tracey-Widom test.}
\end{figure}

\begin{figure}[H]
\includegraphics[scale=.4]{figures/supplemental/synteny_chinook.png}
\caption{Oxford grid - Chum and Chinook linkag groups.}
\end{figure}
